---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# trlboku

**t**ree **r**ing **l**ab **boku** - is a development version package for R

This package holds a collection of functions and data used
	at the tree ring lab at BOKU, University of Natural Resources and Life 
	Sciences, for internal use. The package is not intended to address an
	explicit topic but rather gathers functions related to
	dendroclimatology, data manipulation, dendrochronological dating and
	so on.
	
## Installation

You can install trlboku from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("konradmayer/trlboku")
```


## Coming soon ...
Further function implementations as well as vignettes and examples in the
function documentations will be added in near future, please refer to 
the package history. If a needed function is missing please file an issue or 
write an email.

## Updating

subsequent implementations and bug fixes require regular updating, to keep your
installation up to date type:

```{r gh-update, eval = FALSE}
devtools::update_packages("trlboku")
```
